When are Fuzzy Extractors Possible?

### 2014-10-06 trunk/info-bounds/FuzzyExtPossibility.tex
adding revised proof of lower bounds to appendix

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}
\DeclareMathOperator*{\var}{\text{Var}}

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\key}{\ensuremath{\class{key}}\xspace}
\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\crust}{\ensuremath{\class{Crust}}\xspace}
\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}
\newcommand{\eqdef}{\stackrel{\rm def}{=}}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. To help eliminate noise, they produce a non secret helper string. This helper value allows the key to be regenerated from a nearby point.  Known constructions of fuzzy extractors do not provide security for most noisy distributions that occur in practice.

The nonsecret helper string allows an adversary to learn the generated key if they can guess a point close to the original reading.  A necessary condition to derive keys from a distribution is that no adversary can guess nearby points.  We call this condition \emph{fuzzy min-entropy}.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.  In this work, we ask whether fuzzy min-entropy is a sufficient condition for security in the fuzzy extractor setting.

A key impediment to providing security is distributional uncertainty.  We consider two settings, first where the fuzzy extractor knows the precise distribution and second the fuzzy extractor knows the distribution comes from some family.  We show that fuzzy min-entropy is a sufficient condition in the first setting and insufficient in the second setting.  That is, there is families of distributions with fuzzy min-entropy that no fuzzy extractor can derive keys from.  Our results are information-theoretic.

\bnote{keep editing}
\end{abstract}

@@

The security requirement for fuzzy extractors that is $\key$ uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \le \Hfuzz(W) \le \Hoo(W)-\log |B_t(\cdot)|$ with equality when $t=0$.

Super-logarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(we show this in  \lemref{lem:fuzz necessary}, which formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t(\cdot)|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz$ as the right measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t(\cdot)|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by simply applying a randomness extractor.) On the other hand, there is a family of sources with superlogarithmic $\Hfuzz=\Hoo$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ''levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
Note constructing a family of distributions $\mathcal{W}$ and proving impossibility for a uniformly random (rather than worst-case) $W\in \mathcal{W}$  is sufficient.
We start by observing the following asymmetry: $\gen$  see only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space.

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $\sketch$ can be used to find fixed points of $\rec(\cdot, \sketch)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

We note that the use of a high-dimensional Hamming space is important: fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

\lnote{old two pars below this line --- do we need anything?}

We construct a family of distributions $\mathcal{W}$ for which knowing only a single value $w$ leaves the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

 The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.  Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.

\bnote{are these really affine lines?}
\bnote{I'm writing these, very rough draft}

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
 Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

>>>>

\newcommand{\secref}[1]{\mbox{Section~\ref{#1}}}
\newcommand{\subsecref}[1]{\mbox{Subsection~\ref{#1}}}
\newcommand{\apref}[1]{\mbox{Appendix~\ref{#1}}}
\newcommand{\thref}[1]{\mbox{Theorem~\ref{#1}}}
\newcommand{\exref}[1]{\mbox{Example~\ref{#1}}}
\newcommand{\defref}[1]{\mbox{Definition~\ref{#1}}}
\newcommand{\corref}[1]{\mbox{Corollary~\ref{#1}}}
\newcommand{\lemref}[1]{\mbox{Lemma~\ref{#1}}}
\newcommand{\assref}[1]{\mbox{Assumption~\ref{#1}}}
\newcommand{\probref}[1]{\mbox{Problem~\ref{#1}}}
\newcommand{\clref}[1]{\mbox{Claim~\ref{#1}}}
\newcommand{\propref}[1]{\mbox{Proposition~\ref{#1}}}
\newcommand{\remref}[1]{\mbox{Remark~\ref{#1}}}
\newcommand{\consref}[1]{\mbox{Construction~\ref{#1}}}
\newcommand{\figref}[1]{\mbox{Figure~\ref{#1}}}
\DeclareMathOperator*{\expe}{\mathbb{E}}
\DeclareMathOperator*{\var}{\text{Var}}
\DeclareMathOperator*{\argmax}{arg\,max}

\newcommand{\class}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\key}{\ensuremath{\class{key}}\xspace}
\newcommand{\Key}{\ensuremath{\class{Key}}\xspace}

\newcommand{\gen}{\ensuremath{\class{Gen}}\xspace}
\newcommand{\rep}{\ensuremath{\class{Rep}}\xspace}
\newcommand{\sketch}{\ensuremath{\class{SS}}\xspace}
\newcommand{\rec}{\ensuremath{\class{Rec}}\xspace}
\newcommand{\enc}{\ensuremath{\class{Enc}}\xspace}
\newcommand{\dec}{\ensuremath{\class{Dec}}\xspace}
\newcommand{\prg}{\ensuremath{\class{prg}}\xspace}
\newcommand{\crust}{\ensuremath{\class{Crust}}\xspace}
\newcommand{\inter}{\ensuremath{\class{Inter}}\xspace}
\newcommand{\zo}{\ensuremath{\{0, 1\}}}
\newcommand{\vect}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\zq}{\ensuremath{\mathbb{Z}_q}}
\newcommand{\Fq}{\ensuremath{\mathbb{F}_q}}
\newcommand{\sample}{\ensuremath{\class{Sample}}\xspace}
\newcommand{\neigh}{\ensuremath{\class{Neigh}}\xspace}
\newcommand{\dis}{\ensuremath{\mathsf{dis}}}
\newcommand{\decode}{\ensuremath{\mathsf{Decode}}}
\newcommand{\guess}{\mathsf{guess}}
\newcommand{\eqdef}{\stackrel{\rm def}{=}}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{
Benjamin Fuller\footnote{Email: {\tt bfuller@cs.bu.edu}.  Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.}  \and Leonid Reyzin\footnote{Email: {\tt reyzin@cs.bu.edu}.  Boston University.} \and Adam Smith\footnote{Email: {\tt asmith@cse.psu.edu}.  Pennsylvania State University; work performed while at Boston University's Hariri Institute for Computing and RISCS Center, and Harvard University's
``Privacy Tools'' project.}}
}
\begin{document}
\maketitle

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. After the initial enrollment of a secret, any sufficiently similar value will be converted to the same output key. Therefore, a minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret.

We formalize this property of a noisy source of secrets by defining \emph{fuzzy min-entropy}. High fuzzy min-entropy is clearly necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. In this work, we ask: \emph{is fuzzy min-entropy sufficient to build an information-theoretic fuzzy extractor?} 
%\lnote{Or it seems sufficient under strong computational assumptions and, under weaker assumptions, in the interactive setting.}  
%\lnote{may be use``analyzing this quantity may be more fruitful than analyzing min-entropy and error-tolerance separately''}

We give a positive answer to this question when the fuzzy extractor knows the precise distribution of the physical source.  On the other hand, because it is imprudent to assume a precise knowledge of a complicated distribution,  fuzzy extractors are typically expected to work for families of sources. We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.

We provide similar results for secure sketches, whose goal is not to derive a key, but to recover the original secret from a nearby one.

\bnote{mention secure sketches?}
\bnote{keep editing}
\bnote{nearby or close?  be consistent}
\bnote{I renamed section titles to get rid of distribution aware and oblivious.  don't quite like them}
\lnote{mention computational setting?}
\lnote{mention the typical analysis that separates min-entropy and error-tolerance?}
\end{abstract}

@@

The security requirement for fuzzy extractors is that $\key$ is uniform even to a (computationally unbounded) adversary who has observed $p$.   This requirement is  harder to satisfy as the allowed error tolerance $t$ increases, because it becomes easier for the adversary to guess $\key$ by guessing a $w'$ within distance $t$ of $w$ and running $\rep(w',p)$.

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$ with equality when $t=0$. \bnote{I don't follow this equation, equality also for well-spread distributions}

Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition). 
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

\paragraph{Tight Characterization for the Case of a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

This characterization justifies $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  better than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed before the distribution is fully known, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.  its the same corollary}

On the other hand, there is a family of sources with superlogarithmic $\Hfuzz(W)=\Hoo(W)$ for which no secure sketch correcting even a few errors is possible~(\thref{thm:imposs sketch}). The impossibility result applies even when $\rec$ is allowed to be incorrect with probability up to $1/4$ (as opposed to our fuzzy extractor impossibility result).

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have roughly the same probability.  We call distributions of this type ``nearly flat.''  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguiate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the number of possible hash outputs is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is nearly flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}$ and prove impossibility for a uniformly random $W\in \mathcal{W}$~(instead of proving impossibility for a worst-case $W$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W\leftarrow \mathcal{W}$ and $w\leftarrow W$), while
the adversary knows $W$.   To exploit the asymmetry, we construct $\mathcal{W}$ so that conditioning on the knowledge of $W$ reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on the entire space. \bnote{this isn't quite accurate, the first coordinate is known.  you have no info on the rest of the support}

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

The result for fuzzy extractors is delicate.  The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
The result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
\bnote{this needs work}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for every known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results for secure sketches and fuzzy extractors for families of distributions respectively.

\section{Preliminaries}
\label{sec:preliminaries}
%For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$. % For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$. 
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.
 Unless otherwise noted logarithms are base $2$.
The {\em min-entropy} of $W$ is $\Hoo(W) = -\log(\max_w \Pr[W=w])$,
and the {\em average (conditional)} min-entropy of $W$ given $P$ is  $\Hav(W|P) = -\log(\expe_{p\in P} \max_{w} \Pr[W=w|P=p])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   Let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We use an average case notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
the conditional Hartley entropy of $W |P $ is $\tilde{H}_0(W |P) = \log ( \expe_{p\in P} |\{w | \Pr[W=w |P=p]>0\}|)$.

The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\sd(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $w$} is the set of all points within radius $t$, that is, $B_t(w) = \{w'| \dis(w, w')\leq t\}$.  If the size of a ball in a metric space does not depend on $w$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(w,w') = \{i | w_i \neq w'_i\}$ where $\mathcal{Z}$ is some alphabet.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_\kappa$ denotes the uniformly  distributed random variable on $\{0,1\}^\kappa$.  Throughout this work, we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.
